Counting the Cockroaches in the Walls: Assessing the Severity of Service Failures Through Social Chatter

### 2019-08-02 Paper/README.Rmd

---
title: "Counting the Cockroaches in the Walls or I Know Why the Caged Bird Tweets: Assessing the Severity of Service Failures Through Social Chatter"
output: github_document
---

@@

>>>>

---
title: "Counting the Cockroaches in the Walls: Assessing the Severity of Service Failures Through Social Chatter"
output: github_document
---

@@

Keywords: Social Media, Bayesian Inference, Classification Customer Satisfaction, Services Marketing, Text Analysis
